---
title: "Obtaining and use token for HAM"
subtitle: "hamapi: Collecting Artwork info from Harvard Art Museum"
author: "He Yuxiu"
date: "12/13/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Obtaining and use token for HAM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(hamapi)
```

## hamapi

This vignette covers how to obtain and use Harvard Art Museum API access tokens for use in the `hamapi` package.

The Harvard Art Museums API is a REST-style service designed for developers who wish to explore and integrate the museums’ collections in their projects. In order to use this package, Harvard Art Museum asks you to apply for a token. Detailed explaination can be found at the official website: (https://www.harvardartmuseums.org/collections/api)

- Obtain a personal token
The API uses keys to authenticate requests. Every request must be accompanied by the apikey parameter and an API key.
Please follow the link and input your information: (https://docs.google.com/forms/d/e/1FAIpQLSfkmEBqH76HLMMiCC-GPPnhcvHC9aJS86E32dOd0Z8MpY2rvQ/viewform)

Harvard Art Museum is using an automatic reply system, so you will be receiving an email with your token soon. 

### get_token()
This function will send a pop-up window to ask you for your token. 
```{r}
#Please input your token. (WITHOUT THE ' ')
get_token()

#Congrats! Your token is now saved as a global variable and can be used in other functions in this package. 
```


Enjoy your art journey! 

