---
title: "FAQ"
subtitle: "hamapi: Collecting Harvard Art Museum Data"
author: "Yuxiu He"
date: "12/13/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FAQ}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(hamapi)
```

## The "function get_artwork_info" returns NULL...
```{r}
#> artresult <- get_artwork_info(classification='Prints', size=10)
#>
# NULL
```

#### Solutions

1. Make sure you have run the function token <- get_token() AND assign("token", token, envir = globalenv())
1. The possible reason for this situation is that this package can only run after inputting the corresponding token.
1. Please try download this package from https://github.com/MelodieYuxiuHe/HAM and use devtools::load_all()
1. Make sure your input of token is correct and this package should work now.
1. I apologize for any inconvenience caused. 

Good luck!
